Holomorphic field theories and higher algebra

### 2023-08-15 highervertexops.tex
reworked rep thy stuff a little

The algebra $\sfR$ is naturally an $SL(2)$ representation where the linear span of $z_1$, $z_2$ transforms in the fundamental representation and the linear span of  $\lambda_1$, $\lambda_2$ transforms in the dual (or contragredient) representation.
In particular, with respect to the standard Cartan subgroup, $z_1$ and $\lambda_2$ have weight 1 and $z_2$ and $\lambda_1$ have weight $-1$.
For the Lie algebra, the lowering and raising operators are
\beqn
f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2} \quad\text{and}\quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1}.
\eeqn
These actions determine an $SL(2)$-action on the space of all polynomials $\C[z_i,\lambda_i]$,
which breaks up into a direct sum over the subspaces $V_{a,b}$ of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.
In $V_{a,b}$ , a highest weight vector is $z_1^a \lambda_2^b$.
\owen{Can we identify the others?}

Consider the Laplacian operator
\beqn
\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
\eeqn
acting on $\C[z_i,\lambda_i]$.
\owen{This isn't the image of the quadratic Casimir. In what sense is it the relevant Laplacian? On the other hand, it is a weight zero operator, even if it lowers the bigrading by (1,1).}
Let $H_{a,b} \subset V_{a,b}$ denote the harmonic polynomials of bidegree $(a,b)$.
Examples of harmonic polynomials include $z_1^a \lambda_2^b$ for arbitrary $a,b$ and
$z_1 \lambda_1 - z_2 \lambda_2$ for $a = 1 = b$.
A direct computation shows that there is a direct sum decomposition \owen{of representations?}
\begin{align*}
V_{a,b} & = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1} \\
& = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots 
\end{align*}
(Compare with the well-known construction of spherical harmonics.)

@@

@@

\begin{proof}
\owen{We should write out the proof.}
\end{proof}

@@

\begin{proof}[Proof of proposition]
In fact $\Phi$ maps the subspace $\sfR_{a,b}$ isomorphically to $\cH_{a,b}$ where $\cH_{a,b} \subset \Omega^{0,\bu}_b (S^3)$ is the space of harmonic polynomials that are of bidegree $(a,b)$ in the variables $(w_i,\Bar{w}_j)$.
To see that the differentials are compatible we observe that
\beqn
\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \Phi (\omega) = \xi_i = \dbar_b \Phi (\lambda_i) .
\eeqn
\end{proof}

@@

\begin{cor}
If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
\[
\CC \to \widehat{\fg} \to \fg.
\]
\end{cor}

>>>>

The algebra $\sfR$ is naturally an $SL(2)$ representation where the linear span $V_z$ of $z_1$, $z_2$ transforms in the fundamental representation  and the linear span $V_\lambda$ of  $\lambda_1$, $\lambda_2$ transforms in the dual (or contragredient) representation.
In particular, with respect to the standard Cartan subgroup, $z_1$ and $\lambda_2$ have weight 1 and $z_2$ and $\lambda_1$ have weight~$-1$.

Consider now the space of all polynomials
\[
\C[z_i,\lambda_i] = \Sym(V_z \oplus V_\lambda) \cong \Sym(V_z) \otimes \Sym(V_\lambda).
\]
The Lie algebra $\sl(2)$ acts by the lowering and raising operators
\beqn
f = z_2 \del_{z_1} - \lambda_1 \del_{\lambda_2} \quad\text{and}\quad e = z_1 \del_{z_2} - \lambda_2 \del_{\lambda_1}.
\eeqn
The space of polynomials breaks up into a direct sum over the subrepresentations 
\[
V_{a,b} = \Sym^a(V_z) \otimes \Sym^b(V_\lambda)
\]
of polynomials that are homogenous of order $a$ in the variables $z_i$ and homogenous of order $b$ in the variables~$\lambda_i$.

Recall that $\Sym^a(V_z)$ is an irreducible representation of dimension $a+1$ (and hence highest weight $a$) and $\Sym^b(V_\lambda)$ is an irreducible representation of dimension $b+1$ (and hence highest weight $a$).
Let $I_m$ denote the irreducible representation of highest weight $m$ (and hence of dimension $m+1$).
By standard facts about $SL(2)$, we see that $V_{a,b}$ decomposes as a direct sum of irreducible representations
\[
V_{a,b} \cong I_{a+b} \oplus I_{a+b-2} \oplus \cdots \oplus I_{a-b}
\]
for $a \geq b$. (The other situation can be seen by symmetry.)

There is a more concrete way to describe this decomposition.
Consider the differential operator
\beqn
\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
\eeqn
acting on $\C[z_i,\lambda_i]$.
\owen{This isn't the image of the quadratic Casimir. In what sense is it the relevant Laplacian? On the other hand, it is a weight zero operator, even if it lowers the bigrading by (1,1).}
Let $H_{a,b} \subset V_{a,b}$ denote the harmonic polynomials of bidegree $(a,b)$.
Examples of harmonic polynomials include $z_1^a \lambda_2^b$ for arbitrary $a,b$ and
$z_1 \lambda_1 - z_2 \lambda_2$ for $a = 1 = b$.
A direct computation shows that there is a direct sum decomposition \owen{of representations?}
\begin{align*}
V_{a,b} & = H_{a,b} \oplus |(z,\lambda)|^2 V_{a-1,b-1} \\
& = H_{a,b} \oplus |(z,\lambda)|^2 H_{a-1,b-1} \oplus |(z,\lambda)|^4 H_{a-2,b-2} \oplus \cdots 
\end{align*}
(Compare with the well-known construction of spherical harmonics.)

@@

The following fact is quite useful for us.

@@

This lemma is proved by applying the description of the decomposition into irreducibles.

@@

\begin{proof}[Proof of proposition]
In fact $\Phi$ maps the subspace $\sfR_{a,b}$ isomorphically to $\cH_{a,b}$ where $\cH_{a,b} \subset \Omega^{0,\bu}_b (S^3)$ is the space of harmonic polynomials that are of bidegree $(a,b)$ in the variables $(w_i,\Bar{w}_j)$.
Now observe that
\beqn
\Phi(\dbar(\lambda_i)) = - \Phi(\ep_{ij} z_j \omega) = - \ep_{ij} w_j \Phi (\omega) = \xi_i = \dbar_b \Phi (\lambda_i) 
\eeqn
to see that the differentials are compatible.
\end{proof}

@@

\begin{cor}
If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
\[
\CC \to \widehat{\fg} \to \fg
\]
determined by $J^* \omega$.
\end{cor}
